---
title: "OMI by raw"
author: "Rutger Vos (@rvosa)"
date: "27-5-2020"
output:
  pdf_document: default
  html_document: default
---

Given that wd is in the same location as this file, we can then read the data
as follows:

```{r load}
omi.df <- read.csv('../data/niche_traits_merged.csv', header = T)
raw.df <- read.csv('../data/raw_means.csv', header = T)
```

Next, we have to make sure the observations (rows) have the same names, i.e. the
taxon names from ALLMB. The raw file was written as a CSV without a name for the
labels, so reading it again creates a column X, while the OMI file has a column
called allmb_name:

```{r rows}
row.names(raw.df) <- raw.df$X
row.names(omi.df) <- omi.df$allmb_name
```

Now that the rows have names, we can combine the tables using `merge()`, and
tell it to do the merge by column 0, which are the row names:

```{r merge}
combined <- merge(raw.df,omi.df,by=0)
```

Quick check to see what's what:

```{r check}
row.names(combined) <- combined$Row.names

# after the merger, the Aspect column from raw.df is Aspect.x
raw.df['Acacia ampliceps','Aspect'] == combined['Acacia ampliceps','Aspect.x']

# and the Aspect column from omi.df is Aspect.y
omi.df['Acacia ampliceps','Aspect'] == combined['Acacia ampliceps','Aspect.y']
```

And now we can plot, raw on the x axis, omi on the y:

```{r plot}
plot(combined$Aspect.x,combined$Aspect.y)
plot(combined$BulkDensity.x,combined$BulkDensity.y)
plot(combined$ClayPercentage.x,combined$ClayPercentage.y)
plot(combined$annualPET.x,combined$annualPET.y)
plot(combined$aridityIndexThornthwaite.x,combined$aridityIndexThornthwaite.y)
plot(combined$climaticMoistureIndex.x,combined$climaticMoistureIndex.y)
plot(combined$continentality.x,combined$continentality.y)
plot(combined$embergerQ.x,combined$embergerQ.y)
plot(combined$PETColdestQuarter.x,combined$PETColdestQuarter.y)
plot(combined$PETDriestQuarter.x,combined$PETDriestQuarter.y)
plot(combined$PETseasonality.x,combined$PETseasonality.y)
plot(combined$PETWarmestQuarter.x,combined$PETWarmestQuarter.y)
# etc!
```